Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-27 Article_B11/Article_B11.Rmd
Commit 2024-08-27 07:11

```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
knitr::include_graphics("../images/P-example-years-13.png")
```

>>>>

```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black. The reference green line goes through the origin with a slope of one.", fig.pos='H'}
knitr::include_graphics("../images/P-example-years-12.png")
```
